\chapter{Background review}\label{ch:A}
\section{Product description}
Easy Mektep is a subject management platform developed by our team in favour of schoolchildren, where schoolchildren can easily organize, complete assigned tasks and track their own progress, control one's time consuming habits. Also, it is a platform, where teachers can create classes and upload assignments for students and check them. In addition, due to the plagiarism checker feature, teachers are able to find cheaters and see overall statistics on children's works' uniqueness(antiplagiarism).  \\
The platform should be slightly styled with national patterns, in order to preserve our national style. 
The site presents a multi-level system for organising the lesson content. The lessons were developed with the use of the task-based learning approach. While completing a task of a certain priority, a student is involved in the active cognitive process. Each task provides a short introductory material and bonus announcement system which helps student to effectively concentrate his knowledge on the task and contributes to successful completion of the task.
\section{User requirements }
\vspace{0.4cm}
\subsubsection{To test whether a user story is well formed, we applied the acronym INVEST \cref{app:B}.\cite{buglione2013improving}}
\vspace{1cm}
\large \textbf{User stories}
\vspace{0.4cm}\\
* As a new user, I want to sign up using my existing Google account so that I don't have to keep track of another account.

* As an existing student, I want to see all my tasks, so that I don't miss any of them.

* As a student, I want to break down assigned tasks, and prioritize them, so that I could work effectively.

* As a teacher, I want to create classes, add students to them, and assign them tasks/projects.

* As a teacher, I want to see statistics on plagiarism, to make sure that evaluating process is fare. 

* As a teacher, I want to see students' progress for specific data range. 

* As a student, I want to see time I spent on particular task, so that I can manage my energy and distribute my time wisely.

* As a student, I want to easily use it from any gadget.

* As a student, I want to control your time spent on  studying.
\section{Product Requirements Document - PRD} \label{sec:PRD}
Product should solve outstanding problems in education like lack of motivation, not receiving timely feedback, not receiving clear instructions or expectations. \cref{ch:Ref}\\
Students should be able to understand what advantages the completion of task will provide them. \\
Exam dates, day offs, and other special calendar events should be clearly visible.\\
Teacher info for contacting should be always on hand.\\
Platform should be trustworthy.\\
Students can upload their works.\\
The platform website must be responsive: work well and look good on all screen sizes.\\
The product should have two roles: students and teachers, in order to reduce misunderstandings between a teacher and a student while grading and handing in assignments.\\
Teachers can upload their assignments for students and check them. \\
Teachers can check works for plagiarism.
Students should have answers for the following questions:\\
* What type of material you’ll be covering?\\
* How each type of assignment will be graded?\\
* What are the deadlines?\\
