\chapter{Conclusion}\label{ch:concl}
The purpose of this research was to create a useful, functional platform for schools, enriched with functionalities satisfying both teachers' and pupils' certain needs built in slight kazakh modern national style. Before coming up with this idea, we underestimated how worthy domestic platforms can be. There was an opinion like, there are already a lot of educational platforms, why do we need to create one more? However, as we wanted to maintain and upgrade our national values and as we became aware of issues that currently existing domestic and foreign platforms couldn't solve, we decided it is time to seize an opportunity. And we made a start on it. 

This research let us know that school pupils need an update in the online environment, both in the functionality and user interface experience context. To handle the situation we held questionnaires, interviews, where we've seen dissatisfaction with platforms to certain degree (rate 3.5 out of 5). For instance, leak in security, lack of plagiarism check, no overall view of progress opportunity. However, those are the essential aspects that should be taken into account during studying at school and gaining education in general. We've noticed the significance of this functions after interviewing, querying school pupils, teachers and university staff. 

During the implementation of platform we faced some obstacles during the development of frontend side, in a team with no frontend developer, it was a  challenge for us to combine backend part with frontend part. Nevertheless, our team members have a clear vision of our product's perspective and no hurdle made us stop. As a result we were able to integrate both parts. And we are proud of our work, of our team work strategy!

To conclude, we can say that we have created a useful, user friendly platform, which helps to maintain not only educational habits, but also helps to rise young generation's love to our national values. The viability of platform's functions were approved by teachers, school pupils, which instilled in us more faith and positive attitude towards the vision of our product. 

School is the place where children conceive an idea about gaining education as we mentioned in our introduction part (\cref{ch:intro}). And we feel that children's first impression in school should be as bright and joyfull as it is possible in order to pave the way for future innovations of today's young generation. And these innovations, of course, should be made in favor of our motherland. So, we believe that the platform is able to relief managing, studying, lesson organizing processes at schools by rising their love to our national language, style and worths. 

