\chapter{Discussion}\label{ch:disc}
We faced some issues during implementation like not knowing how to concretize questions aiming to get to the point answers in an effort to shape our vision of a product. We worked in a flexible manner conforming to Agile methodology. It was the right decision we made because during the development phase no one amendments were made to the platform. For instance, we didn't plan to add timer feature, didn't target to add block of text with motivational citates and useful information. But later these features were added after we started to receive responds backing up these ideas. Now, about what we removed. In the third phase of our work, we decided to focus more on student's side rather than on teacher's, finishing up teacher's role just with basic functions. This happened because the way we wanted to implement plagiarism check function was too cumbersome and out of frame of our knowledge, thus it took a lot of our backend developer's time to realize this and we decided to apply our well-known methods using python libraries.    
However, tackling all these issues one by one as a team, brainstorming and making decisions together, we could overcome it. 
As a result, now we can answer the questions that arose in our minds before doing our research:\\
\textbf{What additional opportunities do teachers and children need during the work with domestic online platforms? } \\
* to view syllabys of a subject in advance\\
* to leave comments on student's work\\
* to get statistics about plagiarism\\
* to create classes on the platform\\
* to view overall progress visually\\
* to bind learning process with bonuses system\\
\textbf{What functions are hard to be found in the online education environment?}\\
* to view syllabys of subject in advance\\
* to upload the work\\
* to view assignments\\
* old design\\
\textbf{How to improve the level of productivity of school children?}\\
* by providing clear expectations and instructions\\
* by providing teacher-created videos \cite{bond2020facilitating}.\\
